# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r}
library(plyr)
library(lattice)
rawData <- read.csv("activity.csv")
```


## What is mean total number of steps taken per day?

First, we should remove the missing values.
```{r}
completedData <- complete.cases(rawData)
withoutNaData <- rawData[completedData,]
```

Then we calculate the total number of steps taken each day and make a histogram.

```{r}
totalDailySteps1 <- tapply(withoutNaData$steps, withoutNaData$date, sum)
hist(totalDailySteps1)
```

Next, we calculate the mean and median total numbers of steps taken per day.

```{r}
meanDailySteps1 <- tapply(withoutNaData$steps, withoutNaData$date, mean)
medianDailySteps1 <- tapply(withoutNaData$steps, withoutNaData$date, median)
```

So the mean total numbers of steps taken per day is:
```{r echo=FALSE}
print(meanDailySteps1)
```

And the median total numbers of steps taken per day is :
```{r echo=FALSE}
print(medianDailySteps1)
```

## What is the average daily activity pattern?

First, we should calculate the average number of steps taken per interval.
```{r}
averageIntervalSteps <- tapply(withoutNaData$steps, withoutNaData$interval, mean)
```

Then make the time series plot.
```{r}
averageIntervalSteps <- ldply(as.list(averageIntervalSteps), paste)
names(averageIntervalSteps) <- c("interval", "averagesteps")
plot(averageIntervalSteps$interval, averageIntervalSteps$averagesteps, type = "l")
```

So, the 5-minute interval that contains the maximum number of step is :
```{r echo=FALSE}
print(averageIntervalSteps[averageIntervalSteps$averagesteps == max(averageIntervalSteps$averagesteps),]$interval)
```

## Imputing missing values

First, we should calculate the the total number of missing values.
```{r}
amountMissingValues <- nrow(rawData) - nrow(withoutNaData)
```

So the total number of missing values is :
```{r}
print (amountMissingValues)
```

Then we create a dataset filling in all of the missing values with int **1**.

```{r}
for (i in 1:nrow(rawData)) {
        if (is.na(rawData$steps[i])) {
                rawData$steps[i] = 1
                as.integer(rawData$steps[i])
        }
}
```

Next, we make a histogram of the total number of steps taken each day.
```{r}
totalDailySteps2 <- tapply(rawData$steps, rawData$date, sum)
hist(totalDailySteps2)
```

And calculate the mean and median total number of steps taken per day.
```{r}
meanDailySteps2 <- tapply(rawData$steps, rawData$date, mean)
medianDailySteps2 <- tapply(rawData$steps, rawData$date, median)
```

So the mean total numbers of steps taken per day is:
```{r echo=FALSE}
print(meanDailySteps2)
```

And the median total numbers of steps taken per day is :
```{r echo=FALSE}
print(medianDailySteps2)
```

## Are there differences in activity patterns between weekdays and weekends?

First, we create a new factor varible in the dataset with two levels - "weekday" and "weekend".
```{r}
weekdayData <- weekdays(as.Date(rawData$date))
for (i in 1:length(weekdayData)) {
        if (weekdayData[i] == "星期六" | weekdayData[i] == "星期日") {
                weekdayData[i] = "Weekend"
        } else {
                weekdayData[i] = "Weekday"
        }
}
rawData$weekdayData <- as.factor(weekdayData)
```

Make a panel plot containing a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).
```{r}
weekdaysData <- rawData[rawData$weekdayData == "Weekday",]
weekdayAverageSteps <- tapply(weekdaysData$steps, weekdaysData$interval, mean)
weekdayAverageSteps <- ldply(as.list(weekdayAverageSteps), paste)
names(weekdayAverageSteps) <- c("interval", "steps")
weekdayAverageSteps$weekdayData <- "Weekday"

weekendData <- rawData[rawData$weekdayData == "Weekend",]
weekendAverageSteps <- tapply(weekendData$steps, weekendData$interval, mean)
weekendAverageSteps <- ldply(as.list(weekendAverageSteps), paste)
names(weekendAverageSteps) <- c("interval", "steps")
weekendAverageSteps$weekdayData <- "Weekend"

avergeSteps <- data.frame()
avergeSteps <- rbind(avergeSteps, weekdayAverageSteps)
avergeSteps <- rbind(avergeSteps, weekendAverageSteps)
avergeSteps$interval <- as.numeric(avergeSteps$interval)
avergeSteps$steps <- as.numeric(avergeSteps$steps)
avergeSteps$weekdayData <- as.factor(avergeSteps$weekdayData)

xyplot(avergeSteps$steps ~ avergeSteps$interval | avergeSteps$weekdayData, layout = c(1,2),
       panel = function(x, y){
               panel.xyplot(x, y, type = "l")
       })
```